### 2015-01-10 paper/Content/solution.tex
Minor stuff in solution chapter

The interaction with the model is done only by the presenter. This makes the app prototype an implementation of the \emph{Passive View} kind of MVP (see \cite[p. 8]{PassiveMVC}).
An example of an interaction sequence between objects of \texttt{Activity}, \texttt{Presenter} and \texttt{Model} classes is shown in Fig. \ref{fig:androidmvpseq}. Clicking on a button -- let's assume it's labeled \emph{Refresh} -- causes the handler function in the \texttt{Activity} being called. An action is executed on the presenter object by the activity. The presenter retrieves new data from the model and afterwards calls the activity (the \texttt{View}) for showing that data.

@@

As an additional remark, the usage of the \emph{Dependency Injection} (see \cite{Fowler04}) library \emph{Dagger} should be mentioned. The library was used to resolve object dependencies, like the one which exists between an \texttt{Activity} and an \texttt{Presenter} object (and vice versa). It automatically injects references of both objects into each other.

>>>>

The interaction with the model is done only by the presenter. This makes the app prototype an implementation of the \emph{Passive View} kind of MVP.
An example of an interaction sequence between objects of \texttt{Activity}, \texttt{Presenter} and \texttt{Model} classes is shown in Fig. \ref{fig:androidmvpseq}. Clicking on a button -- let's assume it's labeled \emph{Refresh} -- causes the handler function in the \texttt{Activity} being called. An action is executed on the presenter object by the activity. The presenter retrieves new data from the model and afterwards calls the activity (the \texttt{View}) for showing that data.

@@

As an additional remark, the usage of the \emph{Dependency Injection} (see \cite{FowlerIoC}) library \emph{Dagger} should be mentioned. The library was used to resolve object dependencies, like the one which exists between an \texttt{Activity} and an \texttt{Presenter} object (and vice versa). It automatically injects references of both objects into each other.
